Towards human SuperEEG

### 2018-10-04 paper/main.tex

We first applied fourth order Butterworth notch filter to remove 60 Hz
($\pm$ .5 Hz) line noise from every recording (from every electrode).
We then excluded any electrodes that showed putative epileptiform
activity.  Specifically, we excluded from further analysis any
electrode that exhibited an average kurtosis of 10 or greater across
all of that patient's recording sessions.  We also excluded any
patients with fewer than 2 electrodes that passed this criteria, as
the SuperEEG algorithm requires measuring correlations between 2 or
more electrodes from each patient.  For Dataset 1, this yielded clean
recordings from 4168 electrodes implanted throughout the brains of 67
patients (Fig.~\ref{fig:methods}A); for Dataset 2, this yielded clean
recordings from 2975 electrodes from 24 patients.  Each individual
patient contributes electrodes from a limited set of brain locations,
which we localized in a common space~\citep[MNI152;][]{GrabEtal06}; an
example Dataset 1 patient's 54 electrodes that passed the predefined
kurtosis test are highlighted in black and red.

@@

\textbf{JRM STOPPED HERE}

\section*{Results}
To test the accuracy with which the SuperEEG algorithm reconstructs
activity throughout the brain, we held out each electrode from the
full dataset in turn and treated it as unobserved. We then asked: how
closely did each of the SuperEEG-reconstructed LFPs match the observed
data?  We sought to evaluate both the overall reconstruction accuracy
as well as how reconstruction accuracy varied as a function of
implantation location.

We first examined raw LFP traces and their associated Super
EEG-derived reconstructions.  Figure~\ref{fig:recon}A displays the
LFP from the red electrode in Figure~\ref{fig:methods}A, and its
associated reconstruction, during a 5~s time window during one of the
patient's 6 recording sessions.  Figure~\ref{fig:recon}B displays a 2D
histogram of the observed versus reconstructed voltages for every
sample across 14.2 total hours of recordings from that patient (correlation:
$r = 0.91, p < 10\textsuperscript{-10}$).  Although the SuperEEG
algorithm recovered the recordings from this electrode well, we sought to
quantify the algorithm's performance across the full dataset.

>>>>

We first applied fourth order Butterworth notch filter to remove 60 Hz
($\pm$ .5 Hz) line noise from every recording (from every electrode).
Next, we downsampled the recordings (regardless of the original
samplerate) to 250 Hz.  (This downsampling step served to both
normalize for differences in sampling rates across patients and to
ease the computational burden of our subsequent analyses.)  We then
excluded any electrodes that showed putative epileptiform activity.
Specifically, we excluded from further analysis any electrode that
exhibited an average kurtosis of 10 or greater across all of that
patient's recording sessions.  We also excluded any patients with
fewer than 2 electrodes that passed this criteria, as the SuperEEG
algorithm requires measuring correlations between 2 or more electrodes
from each patient.  For Dataset 1, this yielded clean recordings from
4168 electrodes implanted throughout the brains of 67 patients
(Fig.~\ref{fig:methods}A); for Dataset 2, this yielded clean
recordings from 2975 electrodes from 24 patients.  Each individual
patient contributes electrodes from a limited set of brain locations,
which we localized in a common space~\citep[MNI152;][]{GrabEtal06}; an
example Dataset 1 patient's 54 electrodes that passed the predefined
kurtosis test are highlighted in black and red.

@@

\section*{Results}
To test the accuracy with which the SuperEEG algorithm reconstructs
activity throughout the brain, we held out each electrode from the
full dataset in turn and treated it as unobserved. We then asked: how
closely did each of the SuperEEG-estimated recordings at those
electrodes match the observed recordings from those electrodes?

\textbf{JRM STOPPED HERE}
% JRM thoughts:
% - Do we need to use the term "LFP"?
% - Tie in stats from supplemental analyses.  Fig S4: total number of
% electrodes, total number of used electrodes, prop thresholded, total
% recording time, average session time, number of sessions.

We first examined raw LFP traces and their associated SuperEEG-derived
reconstructions.  Figure~\ref{fig:recon}A displays the LFP from the
red electrode in Figure~\ref{fig:methods}A, and its associated
reconstruction, during a 5~s time window during one of the patient's 6
recording sessions.  Figure~\ref{fig:recon}B displays a 2D histogram
of the observed versus reconstructed voltages for every sample across
14.2 total hours of recordings from that patient (correlation:
$r = 0.91, p < 10\textsuperscript{-10}$).  Although the SuperEEG
algorithm recovered the recordings from this electrode well, we sought
to quantify the algorithm's performance across the full dataset.
